Data preprocessing

### 2022-04-13 dev/work/preprocessing.qmd
moved to qmd docs

---
title: "Data preprocessing"
author:
- "Patrick Altmeyer (p.altmeyer@tudelft.nl)"
date: "`r format(Sys.Date(), '%B, %Y')`"
output: 
  bookdown::pdf_document2: 
    toc: false
    includes:
      in_header: ../tex/preamble.tex
  bookdown::html_document2: default
fontsize: 12pt
bibliography: ../bib.bib
link-citations: true
abstract: "..."
---

>>>>

---
title: "Data preprocessing"
author:
- "Patrick Altmeyer (p.altmeyer@tudelft.nl)"
date: "`r format(Sys.Date(), '%B, %Y')`"
---
